---
title: "ModelVis - Classification"
author: "Biswajit Ojha"
output: html_notebook
---

## Model Visualisation

- [0] Visualise the *data space*
- [1] Visualise the *predictions in the data space*
- [2] Visualise the *errors in model fitting*
- [3] Visualise with *different model parameters*
- [4] Visualise with *different input datasets*
- [5] Visualise the *entire model space*
- [6] Visualise the *entire feature space*
- [7] Visualise the *many models together*


## Load the libraries

```{r}
library(broom)
library(MASS)
library(tidyverse)
library(ggthemes)
library(plotly)
library(modelr)
library(DT)
library(ggrepel)
library(rpart)
```


## Set the theme

```{r}
library(ggplot2)
notebook_theme <- theme_fivethirtyeight() + 
         theme( axis.title = element_text(), legend.position = "right",
                  legend.direction = "vertical")
theme_set(notebook_theme)
```

## Read the data

```{r}
setwd("D:/Analytics/Visualization")
cars <- read.csv("cars.csv")
head(cars)
# datatable(cars, options = list())
```

## [0] Visualise the data space

```{r}
c0 <- ggplot(cars) + aes(bhp, price, size = kmpl, color = type) + 
  geom_point()
c0
```

## [1] Visualise the prediction in the data space

Lets make a simple tree model

```{r}
tree <- rpart (type ~ kmpl + bhp + price, cars, method = "class")

summary(tree)

grid <- cars %>%
  data_grid(kmpl = seq_range(kmpl, 25),
                       bhp = seq_range(bhp, 25), price=seq_range(price,25))

pred <- predict(tree, grid, type="prob") %>%
        as.data.frame() %>%
        dplyr::select(Hatchback)

tree_grid <- bind_cols(grid, pred)
colnames(tree_grid)[4] <- "pred"
head(tree_grid) 
  
```

# Plot the data

```{r}
p1 <- ggplot(tree_grid, aes(bhp, price, color=pred)) + geom_point(alpha=0.5) 
p1

```

```{r}

p <- plot_ly(tree_grid, x = ~kmpl, y = ~bhp, z = ~price, color = ~pred) %>%
  add_markers() %>%
  layout(scene = list(xaxis = list(title = 'kmpl'),
                     yaxis = list(title = 'bhp'),
                     zaxis = list(title = 'price')))
p


```