---
title: "R Notebook"
output:
  html_document: default
  html_notebook: default
---


#frame

Two questions
1.Find the State with the highest quantity sales.
2.Predict the daily price for the next 30 days for that state.

#Acquire

we have choosen to scrape data from nfhrd daily basis for 2017

```{r}
getwd()
library(rvest)
library(knitr)
pg.out <- read_html('DailyWiseMarketArrivals.htm')
pg.table <- pg.out %>%
            html_node('#dnn_ctr966_DailyWiseMarketArrivals_GridView1') %>%
            html_table()

df <- pg.table
str(df)

dim(df)  

 ```
#refine

-rename the column name

```{r}
newnames <- c('date','market','quantity','pricemin','pricemax','pricemod')
colnames(df) = newnames
str(df)
```

-remove last row

```{r}
library(dplyr)
tail(df)

df <- df %>%  filter(market != "Total") 

tail(df)

```

-change the datatypes

```{r}
str(df)
df$pricemin <- as.numeric(df$pricemin)
df$pricemax <- as.numeric(df$pricemax)
df$pricemod <- as.numeric(df$pricemod)
df$date <- as.Date(df$date,format ="%d/%b/%Y")
str(df)
```

-cleanup the city name

```{r}
library(stringr)
library(tidyr)
unique(df$market)

df <- df %>%
      mutate(market1= market) %>%
      separate(market1, c('city', 'state'), sep="\\(")
head(df)
df$state <- df$state %>% str_replace("\\)","")
str(df)

# Also, we can drop the market column
#df$market = NULL

df <- df %>%
      mutate(date1= date) %>%
      separate(date1, c('year','month', 'day'), sep="\\-")
head(df)
str(df)
unique(df$state)

```

# Transform


```{r}
library(dplyr)
head(df)

dfState2017 = df %>% group_by(state) %>%
       summarise(quantity_state = sum(quantity)) %>%
       arrange(desc(quantity_state))
dfState2017[1,1]
head(dfState2017)
str(dfState2017)

df.MS_Cities = df %>% group_by(state,city) %>%
              summarise(Quantity=sum(quantity)) %>%  filter(state == 'MS') %>%
                arrange(desc(Quantity))  %>% 
               head(5)
df.MS_Cities
library(ggplot2)
library(plotly)
MS_City_plot = ggplot(df.MS_Cities) + aes(reorder(city,Quantity),weight =Quantity/1000,fill=city) + geom_bar() + coord_flip()    

ggplotly(MS_City_plot)

# Plotting it on map
library(ggmap)
geo =geocode(df.MS_Cities$city)

df.MS_Cities = bind_cols(df.MS_Cities,geo)

map=get_map("India",maptype="watercolor",source="stamen",zoom=5)
ggmap(map)

ggmap(map) + geom_point(data=df.MS_Cities,aes(lon,lat,size=Quantity,color=city))


```


#Explore--The data is presented in wide format,we have to convert it into tall format

```{r}
str(df)
df.MS = df %>%          
        filter(state=='MS',city==df.MS_Cities$city)%>%
        select(date,pricemin,pricemod,pricemax,city,state) %>% 
        gather('PriceType', 'Value',2:4) %>%
        arrange(date)
head(df.MS)
Predict= ggplot(df.MS) + aes(date,Value,color=PriceType) +geom_line() +facet_grid(.~city)

ggplotly(Predict)

```

```{r}
df.Predict = df %>%
             filter(state=='MS',pricemod!=0) %>%
             group_by(date) %>%
             summarise(State_Price=round(mean(pricemod))) %>%
             arrange(date)
colnames(df.Predict) = c('ds','y')
library(prophet)
m= prophet(df.Predict)
future = make_future_dataframe(m,period=30)
forecast =predict(m,future)
ggplotly(plot(m,forecast))

```

