---
title: "ModelVis - Regression"
output:
  html_notebook: default
  html_document: default
---

## Model Visualisation

- [0] Visualise the *data space*
- [1] Visualise the *predictions in the data space*
- [2] Visualise the *errors in model fitting*
- [3] Visualise with *different model parameters*
- [4] Visualise with *different input datasets*
- [5] Visualise the *entire model space*
- [6] Visualise the *entire feature space*
- [7] Visualise the *many models together*


## Load the libraries

```{r}
library(broom)
library(MASS)
library(tidyverse)
library(ggthemes)
library(plotly)
library(modelr)
library(DT)
library(glmnet)
library(ggrepel)
library(dplyr)
library(tidyverse)
```


## Set the theme

```{r}
library(ggplot2)
notebook_theme <- theme_fivethirtyeight() + 
         theme( axis.title = element_text(), legend.position = "right",
                  legend.direction = "vertical")
theme_set(notebook_theme)
```

## Read the data

```{r}
setwd("D:/Analytics/Visualization")
cars <- read.csv("cars.csv")
head(cars)
# datatable(cars, options = list())
```

## [0] Visualise the data space

```{r}
p0 <- ggplot(cars) + aes(kmpl, price, color = type) + geom_point(size = 3)
p0
```

Showing with label names

```{r}
cars$label = paste(cars$brand, cars$model)

set.seed(42)
p0_label <- ggplot(cars) + aes(kmpl, price, color = type) + 
  geom_point(size = 3) +
  geom_text_repel( aes(kmpl, price, label = label ), size = 2.5)
p0_label

```



## [1] Visualise the prediction in the data space

Lets make a simple OLS model

```{r}
lmfit <- lm (price ~ kmpl + type, cars)
lmfit

grid <- cars %>%
  data_grid(kmpl = seq_range(kmpl, 200), type)

str(grid)

lm_grid <- grid %>%
  add_predictions(lmfit, "lm_pred")
head(lm_grid)
```

# Show the prediction in the same data space

```{r}
p1 <- ggplot(cars, aes(kmpl, price, color=type)) + 
  geom_point(size = 3) + 
  geom_line(aes(y=lm_pred, color= type), data = lm_grid, size = 1.5)

p1

```


## [2] Visualise the Errors in Model Fitting

```{r}
cars <- cars %>% 
  add_residuals(lmfit, "lm_resid")


p2 <- ggplot(cars, aes(kmpl, lm_resid, color = type, fill=type)) + 
  geom_point( size = 2) +
  geom_bar(stat="identity", alpha =0.5) +
  facet_wrap(~type)
p2
```


```{r}
p2_alt <- ggplot(cars, aes(kmpl, price, color = type)) + 
  geom_point( size = 1) +
  geom_point( aes(size=abs(lm_resid)), color="red", fill = "white", alpha = 0.2)
p2_alt
```


## [3] Visualise with *different model parameters*

```{r}
x <- cars %>% 
  model_matrix(price ~ kmpl + type) %>%
  as.matrix()

y <- as.double(cars$price)

glm <- cv.glmnet(x, y, alpha= 0.5, standardize=FALSE)

x_grid <- grid %>%
  model_matrix( ~ kmpl + type) %>%
  as.matrix()

glm_pred_min <- predict(glm,x_grid,s="lambda.min") %>%
  as.data.frame() 
colnames(glm_pred_min)[1] <- "glm_min"

glm_pred_1se <- predict(glm, x_grid, s="lambda.1se")  %>%
  as.data.frame() 
colnames(glm_pred_1se)[1] <- "glm_lse"

glm_grid <- bind_cols(grid, glm_pred_min, glm_pred_1se) %>%
  gather("mod", "pred", 3:4)

p3 <- ggplot(cars, aes(kmpl, price, color=type)) +
  geom_point(size = 3) +
  geom_line(aes(y = pred), data=glm_grid, size = 0.5) + 
  facet_wrap(~mod)

p3

tidied_cv <- tidy(glm)
tidied_cv
glance_cv <- glance(glm)

p3_cv <- ggplot(tidied_cv, aes(lambda, estimate)) + geom_line(color = "red") +
    geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2) +
    scale_x_log10() + 
    geom_vline(xintercept = glance_cv$lambda.min) +
    geom_vline(xintercept = glance_cv$lambda.1se, lty = 2)

p3_cv
```


## [4] Visualise with *different input datasets*

```{r}

cars <- cars %>%
  mutate(.id = "000")

lm_function <- function(df) {
  lm(price ~kmpl + type, data = df)
}

boot <- cars %>% 
  modelr::bootstrap(100) %>%
  mutate(model = map(strap, lm_function)) %>%
  mutate(pred = map2(list(grid), model, add_predictions))

p4 <- boot %>%
  unnest(pred) %>%
  ggplot(aes(kmpl, pred, group=.id, color=type)) +
  geom_point(size = 0.1, alpha = 0.1) + 
  geom_point(aes(kmpl, price, color = type), data=cars, size = 3)

p4
```

## [5] Visualise the *entire model space*


## [6] Visualise the *entire feature space*


##[7] Visualise the *many models together*

```{r}

lm2 <- function(df) {
  lm(price ~ kmpl, data = df)
}

grid2 <- cars %>%
  data_grid(kmpl = seq_range(kmpl, 200))

many_models <- cars %>%
  group_by(type) %>%
  nest() %>%
  mutate(model = map(data, lm2))  %>%
  mutate(pred = map2(list(grid2), model, add_predictions))


p7 <- many_models %>%
  unnest(pred) %>%
  ggplot(aes(kmpl, pred, group=type, color=type)) +
  geom_point(size = 1, alpha = 1) + 
  geom_point(aes(kmpl, price, color = type), data=cars, size = 3)
p7

```

## Extending for 5 types

```{r}

cars5 <- read_csv("cars_5.csv")

grid5 <- cars %>%
  data_grid(kmpl = seq_range(kmpl, 200))

many_models5 <- cars5 %>%
  group_by(type) %>%
  nest() %>%
  mutate(model = map(data, lm2))  %>%
  mutate(pred = map2(list(grid2), model, add_predictions))


p7_5 <- many_models5 %>%
  unnest(pred) %>%
  ggplot(aes(kmpl, pred, group=type, color=type)) +
  geom_point(size = 1, alpha = 1) + 
  geom_point(aes(kmpl, price, color = type), data=cars5, size = 3)

p7_5
```



